---
title: <center><b> Stout Case Study </b></center>
subtitle: <center><b> Number 2 </b></center>
author: <center> Sayak Chakraborty </center>
output:
  html_document: 
    code_folding: show
always_allow_html: yes
---

<style>
body {
        text-align: justify;
        font-family: "Bookman", Bookman;
        font-size: 15pt;
     }
</style>

<style>

h1 {
  color: #2100A4;
  font-family: Bookman;
}

h2 {
  color: #2100A4;
  font-family: Bookman;
}

h3 {
  color: #2100A4;
  font-family: Bookman;
}

h4 {
  color: #2100A4;
  font-family: Bookman;
}

a, a:hover {
    color: #C70039 ;
}

</style>


# {.tabset .tabset-fade .tabset-pills}

## 1. **Synopsis**

There is 1 dataset(csv) with 3 years worth of customer orders. There are 4 columns in the csv dataset: index, CUSTOMER_EMAIL(unique identifier as hash), Net_Revenue, and Year.

For each year we need the following information:

*	Total revenue for the current year
*	New Customer Revenue e.g. new customers not present in previous year only
*	Existing Customer Growth, Revenue of existing customers for current year – Revenue of existing customers from existing year
*	Revenue lost from attrition
*	Existing Customer Revenue Current Year
*	Existing Customer Revenue Prior Year
*	Total Customers Current Year
*	Total Customers Previous Year
*	New Customers
*	Lost Customers

Dataset:https://www.dropbox.com/sh/xhy2fzjdvg3ykhy/AADAVKH9tgD_dWh6TZtOd34ia?dl=0


## 2. **Packages Required**

We begin by loading the packages that will be required throughout the course of our analysis.

```{r Loading the required packages, results='hide', echo=TRUE, message=FALSE, warning=FALSE, fig.align='center'}

library(tidyr)
library(DT)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(kableExtra)
library(lubridate)
library(readxl)
library(highcharter)
library(lubridate)
library(scales)
library(RColorBrewer)
library(wesanderson)
library(plotly)
library(shiny)
library(readxl)
library(readr)
library(scales)
library(stringr)
library(boot)
library(reshape2)
```
***

## 3. **Data Preparation** {.tabset .tabset-fade .tabset-pills}

After loading the required packages, we move on to the data preparation step which would start by loading the data into our R-studio.

### 3.1 Loading and Reading the Data 

```{r Loading the data, echo=FALSE, include=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data <- data.table::fread("casestudy2.csv")
str(data)
```

<h2> Summary and Glimpse of the Data </h2>
```{r Summary and Glimpse of the Data, echo=TRUE, message=FALSE, warning=FALSE, fig.align='center'}
summary(data)
glimpse(data)
```

<h3> Observations </h3>


<h2> Checking for NA </h2>

Next we will check for missing values and deal with them accordingly. 
```{r Checking for NA, echo=TRUE, message=FALSE, warning=FALSE, fig.align='center'}
summary(is.na(data))
```

<h3> Observations </h3>

### 3.3 Cleaned Dataset

The final cleaned dataset can be found below in an interactive table.


```{r Datatable, echo=TRUE,  message=FALSE, warning=FALSE, fig.align='center' }
datatable(head(data, 20), class = 'cell-border stripe')
```

****

## **Task**

<h1> 1. Total revenue for the current year </h1>

```{r}

data %>%
group_by(year) %>%
summarise(Revenue =sum(net_revenue))
```
 <h3> Answer </h3>
 
 The Current Revenue of 2017 is **$31417495**
 
 
 <h1> •	New Customer Revenue e.g. new customers not present in previous year only </h1>

```{r}

cust_2017 <- data %>% 
  filter( year == 2017) 

cust_2016 <- data %>% 
  filter( year == 2016)

cust_2015 <- data %>% 
  filter( year == 2015)


new_cust_2017 <- anti_join(cust_2017, cust_2016, by = c("customer_email" = "customer_email"))
new_cust_2016 <- anti_join(cust_2016, cust_2015, by = c("customer_email" = "customer_email"))

new_cust_2017 %>%
summarise(Revenue_new_cust_2017 = sum(net_revenue))

new_cust_2016 %>%
summarise(Revenue_new_cust_2016 = sum(net_revenue))

```
 
<h1> •	Existing Customer Growth, Revenue of existing customers for current year – Revenue of existing customers from existing year </h1>

```{r}

result = data %>% 
  group_by(customer_email) 

head(result)
```

